---
title: "Summary Report"
author: "Grounded Solutions Network"
date: "`r Sys.Date()`"
output: html_document
params:
  place: NA
  
  zhvi: NA
  zhvi_onebd: NA
  zhvi_twobd: NA
  zhvi_threebd: NA
  zhvi_fourbd: NA
  zhvi_fivebd: NA 
              
  zfhg_one: NA
  zfhg_two: NA
  zfhg_three: NA
  
  pct_five: NA
  onebd_pct_change_table: NA
  twobd_pct_change_table: NA
  threebd_pct_change_table: NA 
  fourbd_pct_change_table: NA
  fivebd_pct_change_table: NA 

  pct_avg: NA
  onebd_pct_avg_table: NA
  twobd_pct_avg_table: NA
  threebd_pct_avg_table: NA
  fourbd_pct_avg_table: NA 
  fivebd_pct_avg_table: NA 
---
## Selected Geography
```{r,echo=FALSE}
print(params$place)

```

## Real Estate Market Trends

### Zillow Home Value Index for Single-Family Homes
```{r,echo=FALSE}
params$zhvi
```

### Annual Percent Change in Home Value for Single-Family Homes
```{r, echo=FALSE}
params$pct_five
```

### Average Percent Change in Home Value for Single-Family Homes
```{r, echo=FALSE}
params$pct_avg
```

### Zillow Home Value Index for One Bedrooms (All Home Types)
```{r,echo=FALSE}
params$zhvi_onebd
```

### Annual Percent Change in Home Value for One Bedrooms (All Home Types)
```{r, echo=FALSE}
params$onebd_pct_change_table
```

### Average Percent Change in Home Value for One Bedrooms (All Home Types)
```{r, echo=FALSE}
params$onebd_pct_avg_table
```


### Zillow Home Value Index for Two Bedrooms (All Home Types)
```{r,echo=FALSE}
params$zhvi_twobd
```

### Annual Percent Change in Home Value for Two Bedrooms (All Home Types)
```{r, echo=FALSE}
params$twobd_pct_change_table
```

### Average Percent Change in Home Value for Two Bedrooms (All Home Types)
```{r, echo=FALSE}
params$twobd_pct_avg_table
```

### Zillow Home Value Index for Three Bedrooms (All Home Types)
```{r,echo=FALSE}
params$zhvi_threebd
```

### Annual Percent Change in Home Value for Three Bedrooms (All Home Types)
```{r, echo=FALSE}
params$threebd_pct_change_table
```

### Average Percent Change in Home Value for Three Bedrooms (All Home Types)
```{r, echo=FALSE}
params$threebd_pct_avg_table
```

### Zillow Home Value Index for Four Bedrooms (All Home Types)
```{r,echo=FALSE}
params$zhvi_fourbd
```

### Annual Percent Change in Home Value for Four Bedrooms (All Home Types)
```{r, echo=FALSE}
params$fourbd_pct_change_table
```

### Average Percent Change in Home Value for Four Bedrooms (All Home Types)
```{r, echo=FALSE}
params$fourbd_pct_avg_table
```

### Zillow Home Value Index for Five Bedrooms (All Home Types)
```{r,echo=FALSE}
params$zhvi_fivebd
```

### Annual Percent Change in Home Value for Five Bedrooms (All Home Types)
```{r, echo=FALSE}
params$fivebd_pct_change_table
```

### Average Percent Change in Home Value for Five Bedrooms (All Home Types)
```{r, echo=FALSE}
params$fivebd_pct_avg_table
```




### Zillow Forecasted Value Growth for All Home Types
Feb 28, 2023 forecasted growth: 
```{r,echo=FALSE}
params$zfhg_one
```

Apr 30, 2023 forecasted growth:
```{r,echo=FALSE}
params$zfhg_two
```

Jan 31, 2024 forecasted growth:
```{r,echo=FALSE}
params$zfhg_three
```
